---
title: "Step by Step Analysis"
date: "(`r format(Sys.time(), '%d %b %Y')`)"
author: "Taylor Lab"
output: 
  html_document:
    toc: true
    code_folding: "hide"
    df_print: kable
---

### Loading the necessary libraries and packages

```{r}
library(pacman)
pacman::p_load(data.table, ggplot2, lubridate, stringr, ggpubr, dplyr, cowplot, readxl, scales, knitr, tidyr)
```

### Set paths to input and output

1.  Where do you store your all of the **plate folders** containing the excel files?
2.  Output files will be stored in the same location!
3.  Do you want to store the created **figures** here or somewhere else?

```{r}
Input_Directory <- "./ALL_PLATES/"
save_to         <- Input_Directory
```

4.  Add your cell line names for plots

In the lab we all know that cl204 is our triple KO cell line that lacks MyD88/IRAK4/IRAK1. However, it is likely cryptic to other readers. In addition, many of us use slightly different names, but mean the same thing.. To make plots that can be published and unify all sorts of synonyms, you may want to rename your cell lines in a reproducible manner. For this purpose, take a look at the **ELISA_CL_KEY.csv** and add your names!

```{r}
# adjust the names as needed!
NAME_KEY_DOC <- fread("./ELISA_CL_KEY_DOC.csv", header = T, sep = ",", quote = "")
head(NAME_KEY_DOC, n = 10)

NAME_KEY     <- fread("https://raw.githubusercontent.com/tlobnow/coding_universe/main/Synthetic_Myddosome_Manuscript/SCRIPTS/ELISA_CL_KEY.csv", header = T) 
head(NAME_KEY, n = 10)
```

5.  We will need several functions to analyze the data. You do not need to change this.

```{r}
source(file = ifelse(exists("https://raw.githubusercontent.com/tlobnow/coding_universe/main/scripts/ELISA_Fx.R"), 
                     yes =  "https://raw.githubusercontent.com/tlobnow/coding_universe/main/scripts/ELISA_Fx.R",
                     no  =  "./scripts/ELISA_Fx.R"))
```

### From raw measurements to estimated sample concentrations

1.  Calculate the mean values per Standard Curve dilution step
2.  Plot the Standard curve and fit a linear trend line
3.  Save the plots

We use the equation to estimate IL-2 conc. of our unknown samples

Run ELISA_Fx() to generate standard curves and calculate the IL-2 concentrations.

```{r, echo = F, warning = F, message = F}
All_plates_data_raw <- ELISA_Fx(Input_Directory, Output_Directory)
All_plates_data     <- left_join(All_plates_data_raw, NAME_KEY)
All_plates_data     <- All_plates_data %>% filter(CELL_LINE != "NA")
DF                  <- All_plates_data
```

### Example #1 IL-2 ELISA (normal Plate Check)

In the first example data set, we are checking the **results of the ELISA assay**, so the entire **plate**. In order to process and plot this data, you need to provide some information. First of all, we need to know the Date you want to check. Supply the date as follows: "YYYY-MM-DD". Since we are looking at dates, the filter type must be set to "DATE" (Below you can also find a tutorial where the filter type differs to check for specific cell lines across several experiments).

1.  We want to filter for our **date** of interest "2022-06-09"
2.  Accordingly, we set the filter **type** to "DATE"
3.  Supply the name of your **positive control**, here "WT_EL4" - you can provide either plate names (CELL_LINE) or the plotting names (CL_NAME_ON_PLOT)
4.  Supply the name of your **negative control**, here "tKO_EL4"

```{r, message = F, warning = F}
FILTER_VALUES = "2022-06-09"
FILTER_TYPE   = "DATE" # or "COHORT"
POSITIVE_CTRL = c("WT_EL4")
NEGATIVE_CTRL = c("tKO_EL4", "204_TRIPLE_KO")
COLOR         = "cornflowerblue"
x_label       = ""
y_label       = "relative IL-2 conc."
plot_title    = "IL-2 ELISA"
subtitle      = paste0("Assay performed for ", FILTER_VALUES, ", based on filter type ", FILTER_TYPE)
save          = T

# Automatic settings
DF = All_plates_data
DF$CL_NAME_ON_PLOT = reorder(DF$CL_NAME_ON_PLOT, -DF$ORDER_NO)

SEED = 600
plot_pval = T
plot_faceted_by_date = F
formatted_date <- format(as.IDate(FILTER_VALUES), "%Y%m%d")

# processing ELISA
ALL_COHORT_DATA <- lapply(FILTER_VALUES, function(FILTER_VALUE) {
  # Step 1: Filter & Subset the main data into lists
  COHORT_DATA <- filter_data(DF, FILTER_VALUE, FILTER_TYPE, POSITIVE_CTRL, NEGATIVE_CTRL)
  # Step 2 and Step 3
  NORMALIZED_DATA <- calculate_baseline_and_control(COHORT_DATA, FILTER_TYPE, POSITIVE_CTRL, NEGATIVE_CTRL)
  return(NORMALIZED_DATA)
})

# Step 4: Combine the subset lists into one data frame
COMBINED_DATA <- bind_rows(ALL_COHORT_DATA)

# Step 5: Calculate the means per cohort
MEANS <- COMBINED_DATA %>%
  group_by(CELL_LINE, CONDITION, Date) %>%
  distinct(triplicate_mean_per_day, STIM_DAY, .keep_all = TRUE) %>%
  ungroup()

MEANS$STIM_DAY <- as.factor(MEANS$STIM_DAY)


# Step 6: Calculate the mean of means (MOM) per cohort
MOM_SUBSET <- MEANS %>%
  group_by(CELL_LINE, CL_NAME_ON_PLOT, CONDITION, Date) %>%
  summarise(triplicate_sd_per_day = sd(triplicate_mean_per_day),
            triplicate_mean_per_day = mean(triplicate_mean_per_day)) %>%
  distinct(.keep_all = TRUE)

# Step 7: Perform statistics per cohort
STATISTICAL_RESULTS <- perform_statistical_analysis(MEANS, "CL_NAME_ON_PLOT")

# Step 8: Plotting
my_plot <- ggplot(MEANS, aes(x = CL_NAME_ON_PLOT)) +
  geom_col(data = MOM_SUBSET,
           aes(y = triplicate_mean_per_day, fill = CONDITION), position = position_dodge(width = 1), alpha = 0.5) +
  geom_point(data = MEANS,
             aes(y = triplicate_mean_per_day, group = CONDITION, shape = STIM_DAY),
             position = position_jitterdodge(jitter.height = 0, jitter.width = 1.2, seed = SEED),
             col = "white", size = 4) +
  geom_point(data = MEANS, aes(y = triplicate_mean_per_day, group = CONDITION, shape = STIM_DAY),
             position = position_jitterdodge(jitter.height = 0, jitter.width = 1.2, seed = SEED),
             col = "black", size = 3) +
  geom_errorbar(data = MOM_SUBSET, aes(ymin = triplicate_mean_per_day - triplicate_sd_per_day,
                                       ymax = triplicate_mean_per_day + triplicate_sd_per_day, group = CONDITION),
                width = 0.25, position = position_dodge(width = 1)) +
  labs(x = x_label, y = y_label) +
  scale_fill_manual(values = c("UNSTIM" = "gray50", "STIM" = COLOR)) +
  ggtitle(plot_title) +
  theme_cowplot() +
  theme(legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # geom_text(data = data.frame(CL_NAME_ON_PLOT = names(STATISTICAL_RESULTS[["annotations"]]), y = max(MEANS$triplicate_mean_per_day) + 0.1, label = STATISTICAL_RESULTS[["annotations"]]), aes(y = y, label = label), col = "gray40", size = 4) +
  # geom_text(data = data.frame(CL_NAME_ON_PLOT = names(STATISTICAL_RESULTS[["p_values"]]), y = max(MEANS$triplicate_mean_per_day) + 0.2, label = STATISTICAL_RESULTS[["p_values"]]), aes(y = y, label = label), size = 7) +
  coord_flip() +
  facet_wrap(~Date)

my_plot

if (save) {
  # Step 9: Create Output Folder
  folder_path <- file.path(save_to, paste0("Plate_1_", formatted_date))
  if (!dir.exists(folder_path)) {dir.create(folder_path, recursive = TRUE)}   # Check if the folder exists, and if not, create it
  
  # Step 10: Save Plots and Data
  save_plots(folder_name = basename(folder_path), plots = list(my_plot))
  fwrite(COMBINED_DATA,       file = paste0(folder_path, "/COMBINED_DATA.csv"),       append = F, quote = F, row.names = F, col.names = T)
  fwrite(MEANS,               file = paste0(folder_path, "/MEANS.csv"),               append = F, quote = F, row.names = F, col.names = T)
  fwrite(MOM_SUBSET,          file = paste0(folder_path, "/MOM_SUBSET.csv"),          append = F, quote = F, row.names = F, col.names = T)
  fwrite(STATISTICAL_RESULTS, file = paste0(folder_path, "/STATISTICAL_RESULTS.csv"), append = F, quote = F, row.names = F, col.names = T)
}
```

### Example #2 IL-6 ELISA (normal Plate Check)

```{r, message = F, warning = F}
FILTER_VALUES = c("2023-11-21")
FILTER_TYPE = "DATE"
save = T

x_label     = ""
y_label     = "relative  IL-6 secretion"
plot_title  = "IL-6 secretion of mMPh wt vs. MyD88/IRAK4 dKO"
subtitle    = paste0("Assay performed on ", FILTER_VALUES)

POSITIVE_CTRL = 0
NEGATIVE_CTRL = 0
subtitle = paste0("Assay performed on ", FILTER_VALUES)
SEED = 600
plot_pval = T
plot_faceted_by_date = F
group_vars <- c("CELL_LINE", "CL_NAME_ON_PLOT", "CONDITION")
extra_var <- "STIM_DAY" 
formatted_date <- format(as.IDate(FILTER_VALUES), "%Y%m%d")

filter_pattern_func <- if (FILTER_TYPE %in% "COHORT") {
    print("plot_dose_response_ELISA_2() is currently optizimed for 'DATE' inputs only. Please adjust your input accordingly to use this function.")
  } else if (FILTER_TYPE %in% "DATE") {
    function(value, df) matches_any_pattern_vec(df$Date, value)
  } else {
    stop("Invalid FILTER_TYPE. Must be either 'COHORT' or 'DATE'.")
  }

plates_list <- lapply(FILTER_VALUES, function(value) {
    DF %>%
      filter(filter_pattern_func(value, DF)) %>%
      distinct(Plate) %>%
      pull(Plate)
  })
  
dates_list <- lapply(FILTER_VALUES, function(value) {
    DF %>%
      filter(filter_pattern_func(value, DF)) %>%
      distinct(Date) %>%
      pull(Date)
  })
  
stim_list <- lapply(FILTER_VALUES, function(value) {
    DF %>%
      filter(filter_pattern_func(value, DF)) %>%
      distinct(STIM_DAY) %>%
      pull(STIM_DAY)
  })
  
condition_list <- lapply(FILTER_VALUES, function(value) {
    DF %>%
      filter(filter_pattern_func(value, DF)) %>%
      distinct(CONDITION) %>%
      pull(CONDITION)
  })
  
# Adding names to the list elements
names(plates_list)    <- FILTER_VALUES
names(dates_list)     <- FILTER_VALUES
names(stim_list)      <- FILTER_VALUES
names(condition_list) <- FILTER_VALUES
  
# Create subset based on the lists
subset_list <- lapply(names(plates_list), function(value) {
    plates <- plates_list[[value]]
    dates  <- dates_list[[value]]
    stim   <- stim_list[[value]]
    cond   <- condition_list[[value]]
    
    DF %>%
      filter(Date %in% dates,
             Plate %in% plates,
             STIM_DAY %in% stim,
             CONDITION %in% cond,
             filter_pattern_func(c(POSITIVE_CTRL, NEGATIVE_CTRL, value), DF))
})

# Combine the subsets and return
FILTERED_SUBSET <- bind_rows(subset_list)
group_vars      <- c("Date", "STIM_DAY", "Plate")

DATA_NORMALIZED <- FILTERED_SUBSET %>%
    group_by(Date, Plate) %>%
    filter(Date == FILTER_VALUES) %>%
    mutate(baseline_control_value =  min(Concentration),
           Concentration_REDUCED  = Concentration - baseline_control_value,
           Concentration_REDUCED  = case_when(Concentration_REDUCED < 0 ~ 0, TRUE ~ Concentration_REDUCED)) %>%
    ungroup() %>%
    group_by(Plate) %>%
    mutate(max_control_value = max(Concentration),
           Concentration_REDUCED_NORMALIZED = Concentration_REDUCED/max_control_value)

DATA_NORMALIZED <- DATA_NORMALIZED %>%
  group_by(CELL_LINE, CONDITION, STIM_DAY) %>%
  mutate(triplicate_mean_per_day = mean(Concentration_REDUCED_NORMALIZED),
         triplicate_sd_per_day   = sd(Concentration_REDUCED_NORMALIZED))


# Set the dodge width
dodge_width  <- 0.9
jitter_width <- 0.3


plot1_CONDITION_Concentration_REDUCED_NORMALIZED <- ggplot(DATA_NORMALIZED, aes(x = CONDITION, y = Concentration_REDUCED_NORMALIZED, fill = CELL_LINE, group = CELL_LINE)) +
  geom_col(position = position_dodge(width = dodge_width)) +
  facet_wrap(~paste0(STIM_DAY, "h")+ DILUTION, nrow = 1) +
  labs(x = x_label, y = y_label) +
  ggtitle(label = plot_title, subtitle = subtitle) +
  theme_cowplot() +
  theme(legend.position = "bottom")

plot1_CONDITION_Concentration_REDUCED_NORMALIZED


plot2_STIM_DAY_triplicate_mean_per_day <- ggplot(DATA_NORMALIZED, aes(x = STIM_DAY, y = triplicate_mean_per_day, fill = CONDITION, group = CONDITION)) +
  geom_col(position = position_dodge(width = 1)) +
  facet_wrap(~CELL_LINE+CONDITION, nrow = 1) +
  labs(x = x_label, y = y_label) +
  ggtitle(label = plot_title, subtitle = subtitle) +
  theme_cowplot() +
  theme(legend.position = "bottom", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.x = element_blank())

# plot2_STIM_DAY_triplicate_mean_per_day

if (save) {
  # Step 9: Create Output Folder
  folder_path <- file.path(save_to, paste0("Plate_1_", formatted_date))
  if (!dir.exists(folder_path)) {dir.create(folder_path, recursive = TRUE)}   # Check if the folder exists, and if not, create it
  
  # Step 10: Save Plots and Data
  save_plots(folder_name = basename(folder_path), plots = list(plot1_CONDITION_Concentration_REDUCED_NORMALIZED, 
                                                               plot2_STIM_DAY_triplicate_mean_per_day))
  
  fwrite(COMBINED_DATA,       file = paste0(folder_path, "/COMBINED_DATA.csv"),       append = F, quote = F, row.names = F, col.names = T)
  fwrite(MEANS,               file = paste0(folder_path, "/MEANS.csv"),               append = F, quote = F, row.names = F, col.names = T)
  fwrite(MOM_SUBSET,          file = paste0(folder_path, "/MOM_SUBSET.csv"),          append = F, quote = F, row.names = F, col.names = T)
  fwrite(STATISTICAL_RESULTS, file = paste0(folder_path, "/STATISTICAL_RESULTS.csv"), append = F, quote = F, row.names = F, col.names = T)
}
```

### Example #3 Dose Response ELISA

```{r, message = F, warning = F}
FILTER_VALUE = "2022-11-24"
FILTER_TYPE  = "DATE"
x_label    = "Stimulant Conc."
y_label    = "Relative Response"
plot_title = "Dose Response IL-2 ELISA"
subtitle   = paste0("Assay performed on ", FILTER_VALUES)
save       = T


POSITIVE_CTRL = 0
NEGATIVE_CTRL = 0
subtitle = paste0("Assay performed on ", FILTER_VALUES)
formatted_date <- format(as.IDate(FILTER_VALUE), "%Y%m%d")
SEED = 600
plot_pval = T
plot_faceted_by_date = F
group_vars <- c("CELL_LINE", "CL_NAME_ON_PLOT", "CONDITION")
extra_var <- "STIM_DAY" 


COHORT_DATA <- All_plates_data %>%
  group_by(CELL_LINE, STIM_DAY, CONDITION, Date, Plate) %>%
  filter(Date == FILTER_VALUE)
    
# Calculate baseline values (lowest value per plate)
baseline <- COHORT_DATA %>%
  group_by(Plate) %>%
  filter(Date == as.IDate(FILTER_VALUE)) %>%
  summarise(baseline_control_value = min(Concentration))
    
COHORT_DATA <- left_join(COHORT_DATA, baseline) %>%
  mutate(Concentration_REDUCED = case_when(!is.na(baseline_control_value) ~ Concentration - baseline_control_value, TRUE ~ Concentration))

# Baseline-corrected per cell line, per condition, per stimulation and retrieve the max values to normalize for day-to-day differences.
control_mean_per_day <- COHORT_DATA %>%
      group_by(CELL_LINE, CONDITION, Date, STIM_DAY, Plate) %>%
      reframe(Concentration_REDUCED = Concentration_REDUCED) %>%
      ungroup() %>%
      group_by(STIM_DAY) %>%
      reframe(control_MEASUREMENT = max(Concentration_REDUCED))
    
# Step 5: Normalize the baseline-corrected values by dividing each value by the max value per stimulation day.
COHORT_DATA <- left_join(COHORT_DATA, control_mean_per_day) %>%
      group_by(CELL_LINE, CONDITION, Date, STIM_DAY) %>%
      mutate(Concentration_NORMALIZED = case_when(Concentration_REDUCED / control_MEASUREMENT < 0 ~ 0, TRUE ~ Concentration_REDUCED / control_MEASUREMENT),
             triplicate_mean_per_day = mean(Concentration_NORMALIZED)) %>%
      ungroup()
    
# Make sure that the conditions are now read as numbers for plotting!
COHORT_DATA$CONDITION <- as.numeric(as.character(COHORT_DATA$CONDITION))
  
# Calculate the normalized means per grouped variables (group_vars + extra_vars)
MEANS <- COHORT_DATA %>%
      group_by_at(c(group_vars, extra_var)) %>%
      distinct(triplicate_mean_per_day, STIM_DAY, .keep_all = TRUE) %>%
      ungroup()

# Create a data frame with unique CL_NAME_ON_PLOT and corresponding PLOTTING_COLOR
color_mapping <- unique(MEANS[, c("CL_NAME_ON_PLOT", "PLOTTING_COLOR")])

# Merge the MEANS data frame with the color_mapping data frame using dplyr
MEANS_merged <- MEANS %>%
  left_join(color_mapping) %>%
  mutate(CL_NAME_ON_PLOT = factor(CL_NAME_ON_PLOT, levels = unique(MEANS$CL_NAME_ON_PLOT)))

# Calculate the mean of means (MOM) per cell line and per condition.
MOM_SUBSET <- COHORT_DATA %>%
      group_by(CELL_LINE, CL_NAME_ON_PLOT, CONDITION, PLOTTING_COLOR) %>%
      summarise(triplicate_sd_per_day = sd(triplicate_mean_per_day),
                triplicate_mean_per_day = mean(triplicate_mean_per_day)) %>%
      distinct(.keep_all = TRUE)

# Deriving breaks from unique CONDITION values
condition_breaks <- sort(unique(MOM_SUBSET$CONDITION))
      
PLOT <- ggplot(data = MOM_SUBSET, aes(x = CONDITION, y = triplicate_mean_per_day, group = CELL_LINE, col = CELL_LINE, fill = CELL_LINE)) +
  geom_path(size = 1.5) +
  geom_point(data = MEANS_merged, aes(x = CONDITION, y = triplicate_mean_per_day), size = 3, shape = 21) +
  geom_errorbar(data = MOM_SUBSET, col = "black", linewidth = 0.4, width = 0.25,
                aes(x = CONDITION, y = triplicate_mean_per_day, 
                    ymin = triplicate_mean_per_day - triplicate_sd_per_day, 
                    ymax = triplicate_mean_per_day + triplicate_sd_per_day)) +
  labs(x = x_label, y = y_label) +
  scale_fill_manual(name  = "CELL_LINE", values = setNames(unique(MEANS_merged$PLOTTING_COLOR), unique(MEANS_merged$CELL_LINE))) +
  scale_color_manual(name = "CELL_LINE", values = setNames(unique(MEANS_merged$PLOTTING_COLOR), unique(MEANS_merged$CELL_LINE))) +
  ggtitle(label = plot_title, subtitle = subtitle) +
  theme_cowplot() +
  scale_x_continuous(trans = "log10", breaks = condition_breaks)

PLOT

if (save) {
  # Step 9: Create Output Folder
  folder_path <- file.path(save_to, paste0("DR_Plate_1_", formatted_date))
  if (!dir.exists(folder_path)) {dir.create(folder_path, recursive = TRUE)}   # Check if the folder exists, and if not, create it
  
  # Step 10: Save Plots and Data
  save_plots(folder_name = basename(folder_path), plots = list(PLOT))
  
  fwrite(COMBINED_DATA,       file = paste0(folder_path, "/COMBINED_DATA.csv"),       append = F, quote = F, row.names = F, col.names = T)
  fwrite(MEANS,               file = paste0(folder_path, "/MEANS.csv"),               append = F, quote = F, row.names = F, col.names = T)
  fwrite(MOM_SUBSET,          file = paste0(folder_path, "/MOM_SUBSET.csv"),          append = F, quote = F, row.names = F, col.names = T)
  fwrite(STATISTICAL_RESULTS, file = paste0(folder_path, "/STATISTICAL_RESULTS.csv"), append = F, quote = F, row.names = F, col.names = T)
}

```

### Example #4 Check Cell Lines Across Assays

```{r, message = F, warning = F}
# What to adjust:
FILTER_VALUES = "3E10_GFP"
FILTER_VALUE  = "3E10_GFP"
FILTER_TYPE   = "COHORT"
POSITIVE_CTRL = "WT_EL4"
NEGATIVE_CTRL = "tKO_EL4"
COLOR         = "cornflowerblue"
x_label       = ""
y_label       = "relative IL-2 conc."
plot_title    = "IL-2 ELISA"
subtitle      = paste0("Assay performed for ", FILTER_VALUES, ", based on filter type ", FILTER_TYPE)
save          = F

# Automatic settings
DF = All_plates_data
DF$CL_NAME_ON_PLOT = reorder(DF$CL_NAME_ON_PLOT, -DF$ORDER_NO)
SEED = 600

ALL_COHORT_DATA <- lapply(FILTER_VALUES, function(FILTER_VALUE) {
    # Step 1: Filter & Subset the main data into lists
    COHORT_DATA <- filter_data(DF, FILTER_VALUE, FILTER_TYPE, POSITIVE_CTRL, NEGATIVE_CTRL)
    
    # Step 2 and Step 3
  NORMALIZED_DATA <- calculate_baseline_and_control(COHORT_DATA, FILTER_TYPE, POSITIVE_CTRL, NEGATIVE_CTRL)
  return(NORMALIZED_DATA)
})
  
COMBINED_DATA <- bind_rows(ALL_COHORT_DATA)

# Step 5: Calculate the means per cohort
MEANS <- COMBINED_DATA %>%
    group_by(CELL_LINE, CONDITION, Date) %>%
    distinct(triplicate_mean_per_day, STIM_DAY, .keep_all = TRUE) %>%
    ungroup()

MEANS$STIM_DAY <- as.factor(MEANS$STIM_DAY)

# Step 6: Calculate the mean of means (MOM) per cohort
MOM_SUBSET <- MEANS %>%
    group_by(CELL_LINE, CL_NAME_ON_PLOT, CONDITION, Date) %>%
    summarise(triplicate_sd_per_day = sd(triplicate_mean_per_day),
              triplicate_mean_per_day = mean(triplicate_mean_per_day)) %>%
    distinct(.keep_all = TRUE)

# Step 7: Perform statistics per cohort
STATISTICAL_RESULTS <- perform_statistical_analysis(MEANS, "CL_NAME_ON_PLOT")

# Step 8: Plot the results
plot_cell_line_summary <- ggplot(MEANS, aes(x = CL_NAME_ON_PLOT)) +
    geom_col(data = MOM_SUBSET, aes(y = triplicate_mean_per_day, fill = CONDITION), 
             position = position_dodge(width = 1), alpha = 0.5) +
    geom_point(data = MEANS, aes(y = triplicate_mean_per_day, group = CONDITION, shape = STIM_DAY),
               position = position_jitterdodge(jitter.height = 0, jitter.width = 1.2, seed = SEED), col = "white", size = 4) +
    geom_point(data = MEANS, aes(y = triplicate_mean_per_day, group = CONDITION, shape = STIM_DAY), 
               position = position_jitterdodge(jitter.height = 0, jitter.width = 1.2, seed = SEED), col = "black", size = 3) +
    geom_errorbar(data = MOM_SUBSET, aes(ymin = triplicate_mean_per_day - triplicate_sd_per_day, 
                                         ymax = triplicate_mean_per_day + triplicate_sd_per_day, group = CONDITION), width = 0.25, position = position_dodge(width = 1)) +
    labs(x = x_label, y = y_label) +
  geom_text(data = data.frame(CL_NAME_ON_PLOT = names(STATISTICAL_RESULTS[["annotations"]]), 
                              y = max(MEANS$triplicate_mean_per_day) + 0.1, label = STATISTICAL_RESULTS[["annotations"]]), 
            aes(y = y, label = label), col = "gray40", size = 4) +
  geom_text(data = data.frame(CL_NAME_ON_PLOT = names(STATISTICAL_RESULTS[["p_values"]]), 
                              y = max(MEANS$triplicate_mean_per_day) + 0.2, label = STATISTICAL_RESULTS[["p_values"]]), 
            aes(y = y, label = label), size = 7) +
    scale_fill_manual(values = c("UNSTIM" = "gray50", "STIM" = COLOR)) +
    ggtitle(plot_title) +
    theme_cowplot() +
    theme(legend.position = "bottom") +
    theme(plot.title = element_text(hjust = 0.5))
plot_cell_line_summary

if (save) {
  # Step 9: Create Output Folder
  folder_path <- file.path(save_to, paste0("CL_SUMMARY_", FILTER_VALUES))
  if (!dir.exists(folder_path)) {dir.create(folder_path, recursive = TRUE)}   # Check if the folder exists, and if not, create it
  
  # Step 10: Save Plots and Data
  save_plots(folder_name = basename(folder_path), plots = list(plot_cell_line_summary))
  
  fwrite(COMBINED_DATA,       file = paste0(folder_path, "/COMBINED_DATA.csv"),       append = F, quote = F, row.names = F, col.names = T)
  fwrite(MEANS,               file = paste0(folder_path, "/MEANS.csv"),               append = F, quote = F, row.names = F, col.names = T)
  fwrite(MOM_SUBSET,          file = paste0(folder_path, "/MOM_SUBSET.csv"),          append = F, quote = F, row.names = F, col.names = T)
  fwrite(STATISTICAL_RESULTS, file = paste0(folder_path, "/STATISTICAL_RESULTS.csv"), append = F, quote = F, row.names = F, col.names = T)
}
```

### Other visualization options

So far, we looked at relative secretion plots. This may not be the best data representation. Other options are plotting fold change or real values. The next two examples should show you how to achieve that. We will use the set from to Example #1.

#### Plotting Fold Change

``` {r, message = F, warning = F}

# Step 1: Filter & Subset the main data into lists
COHORT_DATA <- DF[!DF$Is_Dose_Response]
COHORT_DATA <- COHORT_DATA[!grepl("mph", COHORT_DATA$CELL_LINE, ignore.case = TRUE)]

# Step 2: Set negative values to 1 (NOT ZERO)
COHORT_DATA$MEASUREMENT <- ifelse(COHORT_DATA$MEASUREMENT < 0, yes = 1, COHORT_DATA$MEASUREMENT)


# Normalization for fold change from UNSTIM to STIM
NORMALIZED_TO_CONTROL <- COHORT_DATA %>%
  group_by(Date, STIM_DAY, CELL_LINE, CONDITION, CL_NAME_ON_PLOT) %>%
  summarise(mean_per_day = mean(MEASUREMENT),
            Concentration = mean(Concentration))
      
# First, calculate the mean for the UNSTIM condition separately.
unstim_means <- COHORT_DATA %>%
  filter(CONDITION == "UNSTIM") %>%
  group_by(CELL_LINE) %>%
  summarise(mean_unstim = mean(MEASUREMENT))
      
# Now, join this back to the main dataset.
COHORT_SUBSET <- COHORT_DATA %>%
  left_join(unstim_means, by = "CELL_LINE")
      
# Compute the fold change. 
# The `case_when` logic ensures that the fold change is calculated only for the STIM condition.
NORMALIZED_TO_CONTROL <- COHORT_SUBSET %>%
  mutate(fold_change = case_when(CONDITION == "STIM" ~ MEASUREMENT / mean_unstim, TRUE ~ NA_real_ )) %>% # set NA for non-STIM conditions
  ungroup() %>%
  group_by(CELL_LINE, CONDITION) %>%
  mutate(trip_mean = mean(fold_change),
         fold_change_sd = sd(fold_change)) %>%
  unique()
      
# Helper function to perform a t-test and return p-value and annotation
perform_ttest <- function(data) {
  ttest_result <- t.test(data$MEASUREMENT[data$CONDITION == "STIM"],
                         data$MEASUREMENT[data$CONDITION == "UNSTIM"],
                         paired = TRUE)  # or paired = FALSE if the data are independent
  p_value <- ttest_result$p.value
  annotation <- ifelse(p_value < 0.001, '***', 
                       ifelse(p_value < 0.01, '**', 
                              ifelse(p_value < 0.05, '*', 'ns')))
  return(list(p_value = p_value, annotation = annotation))
  }
      
      
results <- COHORT_SUBSET %>%
  group_by(CELL_LINE, CL_NAME_ON_PLOT, Date) %>%
  do({
    data <- .
    fold_change_data <- data %>%
      summarise(fold_change = mean(MEASUREMENT[CONDITION == "STIM"]) / mean(MEASUREMENT[CONDITION == "UNSTIM"]))
    ttest_results <- perform_ttest(data)
    cbind(fold_change_data, ttest_results)
    }) %>%
  ungroup()


# Extract annotations for plotting
annotations        <- results$annotation
names(annotations) <- results$CELL_LINE

# Reorder
results$CELL_LINE = reorder(results$CELL_LINE, -results$fold_change)
      
Date <- as.IDate(unique(results$Date))
# Plotting the fold changes
plot <- ggplot(results, aes(x = CELL_LINE, y = fold_change)) +
  geom_col(position = position_dodge(width = 0.8)) +
  geom_text(aes(label = annotations), 
            # vjust = -0.5) +
            hjust = -0.8) +
  theme_cowplot() +
  theme(legend.position = "bottom") +
  labs(x = "", y = "fold change") +
  coord_flip() +
  facet_wrap(~Date, scales = "free", ncol = 1)

plot

kable(results)

```









