---
title: "Analysis 2024-03-04 ELISA"
date: "`r format(Sys.time(), '%d %b %Y')`"
author: "Taylor Lab"
output: 
  html_document:
    toc: true
    code_folding: "hide"
    df_print: kable
    knitr:
      fig.width: 8
      fig.height: 6
---

### Load necessary libraries and packages
```{r, echo = F, warning = F, message = F}
library(pacman)
pacman::p_load(data.table, ggplot2, lubridate, stringr, ggpubr, dplyr, cowplot, readxl, scales, knitr, tidyr, ggforce, ggbreak, patchwork, lemon)
```

### Source Data & Functions
```{r, echo = T, warning = F, message = F}
Input_Directory <- file.path("/Users/u_lobnow/Desktop/ELISA")
NAME_KEY  <- fread(file.path(Input_Directory, "/ELISA_CL_KEY2.csv"), header = T) 

# load functions
source("~/Documents/Github/Analysis_Synthethic_Myddosome/FigureScripts/functions.R")

process_data_for_plot <- function(data) {
  # Reorder cell lines for plotting
  data$CL_NAME_ON_PLOT <- reorder(data$CL_NAME_ON_PLOT, -data$ORDER_NO)

  # Reformat condition for legend text
  data$CONDITION <- factor(data$CONDITION, levels = c("UNSTIM", "STIM"))
  data$PLOTTING_COLOR[data$CONDITION == "UNSTIM"] <- "#BEBDBD"

  return(data)
}

prepare_plotting_means <- function(data) {
  # Group and summarize data for plotting_means
  plotting_means <- data %>%
    group_by(CELL_LINE, CONDITION, STIM_DAY, CL_NAME_ON_PLOT, PATHWAY, STIMULANT, STIM_CONCENTRATION, PLOTTING_COLOR, ORDER_NO) %>%
    summarise(IL2_concentration_Dilution_Factor_mean = mean(Concentration),
              Relative_Intensity_mean = mean(Concentration_NORMALIZED)) %>%
    as.data.table()

  # Round Relative_Intensity_mean
  plotting_means$Relative_Intensity_mean <- round(plotting_means$Relative_Intensity_mean, 3)

  # Reorder CL_NAME_ON_PLOT
  plotting_means$CL_NAME_ON_PLOT <- reorder(plotting_means$CL_NAME_ON_PLOT, -plotting_means$ORDER_NO)

  return(plotting_means)
}

process_statistical_analysis <- function(data, group_var, value_var) {
  # Perform statistical analysis
  statistical_significance <- perform_statistical_analysis(data, group_var, value_var)

  # Turn statistical_significance list into data.table
  stat_significance_dt <- data.table(
    CL_NAME_ON_PLOT = names(statistical_significance$annotations),
    p_value = statistical_significance$annotations,
    significance = statistical_significance$p_values
  )

  return(stat_significance_dt)
}

prepare_plotting_stats <- function(data, stat_significance_dt) {
  # Group and summarize data for plotting_stats
  plotting_stats_main <- data %>%
    group_by(CELL_LINE, CONDITION, CL_NAME_ON_PLOT, PATHWAY, STIMULANT, STIM_CONCENTRATION, PLOTTING_COLOR, ORDER_NO) %>%
    summarise(
      IL2_concentration_Dilution_Factor_mean = mean(Concentration),
      IL2_concentration_Dilution_Factor_sem = sem(Concentration),
      Relative_Intensity_mean = mean(triplicate_mean_per_day),
      Relative_Intensity_sem = sem(triplicate_mean_per_day)
    ) %>%
    as.data.table() %>%
    left_join(stat_significance_dt)

  plotting_stats_main$CONDITION <- factor(plotting_stats_main$CONDITION, levels = c("UNSTIM", "STIM"))
  plotting_stats_main$CL_NAME_ON_PLOT <- reorder(plotting_stats_main$CL_NAME_ON_PLOT, -plotting_stats_main$ORDER_NO)
  plotting_stats_main$PLOTTING_COLOR[plotting_stats_main$CONDITION == "UNSTIM"] <- "#BEBDBD"

  return(plotting_stats_main)
}


```

### Read Plates
```{r, echo = T, warning = F, message = F}

plate_data_raw <- ELISA_Fx(Input_Directory, Output_Directory)
plate_data     <- left_join(plate_data_raw, NAME_KEY)
plate_data     <- plate_data %>% filter(CELL_LINE != "NA") %>% unique()
plate_data$CONDITION <- as.factor(plate_data$CONDITION)

```


### Manipulate Data & Plot
```{r, echo = T, warning = F, message = F, fig.width=10, fig.height=12}

# Data Subset
Plate_1_and_2      <- plate_data %>% filter(Plate %in% c(1,2) & Date == "2024-03-04")
Plate_1_and_2_data <- process_ELISA_data(DF = Plate_1_and_2, NEGATIVE_CTRL = "cl204", POSITIVE_CTRL = "WT_EL4")

DATA <- Plate_1_and_2_data

# Data Processing
plotting_data_main   <- process_data_for_plot(DATA)
plotting_means       <- prepare_plotting_means(data = plotting_data_main)
stat_significance_dt <- process_statistical_analysis(plotting_means, "CL_NAME_ON_PLOT", "Relative_Intensity_mean")
plotting_stats       <- prepare_plotting_stats(DATA, stat_significance_dt)

kable(stat_significance_dt)

# Data Plotting
X_AXIS <- "Relative IL-2 secretion"
FONT   <- "Helvetica"
SIZE   <- 25
POINTS <- 5
TEXT   <- 8
save   <- TRUE
ZOOM_LOC_X <- 0.2



rel_sec_plot <- ggplot(data = plotting_stats, aes(x = Relative_Intensity_mean, y = CL_NAME_ON_PLOT, fill = PLOTTING_COLOR, group = rev(CONDITION))) +
    geom_col(position = position_dodge(width = 0.7), aes(color = PLOTTING_COLOR), width = 0.68, alpha = 0.3) +
    geom_errorbar(data = plotting_stats, aes(y = CL_NAME_ON_PLOT,
                                             xmin = Relative_Intensity_mean - Relative_Intensity_sem,
                                             xmax = Relative_Intensity_mean + Relative_Intensity_sem),
                  linewidth = .75, position = position_dodge(width = 0.5), width = 0.25) +
    geom_point(data = plotting_means, aes(x = Relative_Intensity_mean, y = CL_NAME_ON_PLOT), 
               shape = 21, size = POINTS, position = position_jitterdodge(dodge.width = 0.5, jitter.width = 0.4, seed = 750), 
               show.legend = FALSE) +
    geom_text(data = plotting_stats, aes(x = max(Relative_Intensity_mean) + 0.11, y = CL_NAME_ON_PLOT, label = significance), 
              hjust = .5, vjust = 1, angle = 90) +
    scale_fill_manual(name  = "CL_NAME_ON_PLOT", values = plotting_stats$PLOTTING_COLOR, breaks = plotting_stats$PLOTTING_COLOR, 
                      labels = ifelse(plotting_stats$CONDITION == "UNSTIM", 
                                      paste0("- ", plotting_stats$STIMULANT), 
                                      paste0("+ ", plotting_stats$STIMULANT))) +
    scale_color_manual(name = "CL_NAME_ON_PLOT", values = plotting_stats$PLOTTING_COLOR, breaks = plotting_stats$PLOTTING_COLOR, 
                       labels = ifelse(plotting_stats$CONDITION == "UNSTIM", 
                                       paste0("- ", plotting_stats$STIMULANT), 
                                       paste0("+ ", plotting_stats$STIMULANT))) +
    labs(x = X_AXIS, y = "") +
    guides(color = "none", fill = guide_legend(reverse = TRUE, ncol = 1)) +
    theme_cowplot(font_size = SIZE, font_family = FONT) +
    theme(axis.text.x       = element_text(size = SIZE, angle = 0, vjust = 0.6),
          axis.title.y      = element_blank(),
          legend.position   = "right",
          legend.title      = element_blank(),
          legend.text       = element_text(size = SIZE),
          legend.key.size   = unit(9, "mm"),
          panel.spacing.x   = unit(-5, "cm"),
          strip.text        = element_text(hjust = 0, face = "bold")) +
  facet_zoom(xlim = c(0, ZOOM_LOC_X), zoom.data = ifelse(a <= ZOOM_LOC_X, NA, FALSE))

rel_sec_plot

```

```{r, echo = T, warning = F, message = F, fig.width=10, fig.height=12}

# Data Subset
Plate_3      <- plate_data %>% filter(Plate == 3 & Date == "2024-03-04")
Plate_3_data <- process_ELISA_data(DF = Plate_3, NEGATIVE_CTRL = "cl204", POSITIVE_CTRL = "cl069")

DATA <- Plate_3_data

# Data Processing
plotting_data_main   <- process_data_for_plot(DATA)
plotting_means       <- prepare_plotting_means(data = plotting_data_main)
stat_significance_dt <- process_statistical_analysis(plotting_means, "CL_NAME_ON_PLOT", "Relative_Intensity_mean")
plotting_stats       <- prepare_plotting_stats(DATA, stat_significance_dt)

kable(stat_significance_dt)

# Data Plotting
X_AXIS <- "Relative IL-2 secretion"
FONT   <- "Helvetica"
SIZE   <- 25
POINTS <- 5
TEXT   <- 8
save   <- TRUE
ZOOM_LOC_X <- 0.2

rel_sec_plot_zoom <- ggplot(data = plotting_stats, aes(x = Relative_Intensity_mean, y = CL_NAME_ON_PLOT, fill = PLOTTING_COLOR, group = rev(CONDITION))) +
    geom_col(position = position_dodge(width = 0.7), aes(color = PLOTTING_COLOR), width = 0.68, alpha = 0.3) +
    geom_errorbar(data = plotting_stats, aes(y = CL_NAME_ON_PLOT,
                                             xmin = Relative_Intensity_mean - Relative_Intensity_sem,
                                             xmax = Relative_Intensity_mean + Relative_Intensity_sem),
                  linewidth = .75, position = position_dodge(width = 0.5), width = 0.25) +
    geom_point(data = plotting_means, aes(x = Relative_Intensity_mean, y = CL_NAME_ON_PLOT), 
               shape = 21, size = POINTS, position = position_jitterdodge(dodge.width = 0.5, jitter.width = 0.4, seed = 750), 
               show.legend = FALSE) +
    geom_text(data = plotting_stats, aes(x = max(Relative_Intensity_mean) + 0.11, y = CL_NAME_ON_PLOT, label = significance), 
              hjust = .5, vjust = 1, angle = 90) +
    scale_fill_manual(name  = "CL_NAME_ON_PLOT", values = plotting_stats$PLOTTING_COLOR, breaks = plotting_stats$PLOTTING_COLOR, 
                      labels = ifelse(plotting_stats$CONDITION == "UNSTIM", 
                                      paste0("- ", plotting_stats$STIMULANT), 
                                      paste0("+ ", plotting_stats$STIMULANT))) +
    scale_color_manual(name = "CL_NAME_ON_PLOT", values = plotting_stats$PLOTTING_COLOR, breaks = plotting_stats$PLOTTING_COLOR, 
                       labels = ifelse(plotting_stats$CONDITION == "UNSTIM", 
                                       paste0("- ", plotting_stats$STIMULANT), 
                                       paste0("+ ", plotting_stats$STIMULANT))) +
    labs(x = X_AXIS, y = "") +
    guides(color = "none", fill = guide_legend(reverse = TRUE, ncol = 1)) +
    theme_cowplot(font_size = SIZE, font_family = FONT) +
    theme(axis.text.x       = element_text(size = SIZE, angle = 0, vjust = 0.6),
          axis.title.y      = element_blank(),
          legend.position   = "right",
          legend.title      = element_blank(),
          legend.text       = element_text(size = SIZE),
          legend.key.size   = unit(9, "mm"),
          panel.spacing.x   = unit(-5, "cm"),
          strip.text        = element_text(hjust = 0, face = "bold")) +
  facet_zoom(xlim = c(0, ZOOM_LOC_X), zoom.data = ifelse(a <= ZOOM_LOC_X, NA, FALSE))

rel_sec_plot_zoom

```


```{r, echo = F, warning = F, message = F}
library(pacman)
pacman::p_load(data.table, ggplot2, lubridate, stringr, ggpubr, dplyr, cowplot, readxl, scales, knitr, tidyr)

################################################################################

# SETTINGS
save   <- F
figure <- "Figure 4/4F/"

################################################################################

# PREPROCESSING
Input_Directory <- file.path("/Volumes/TAYLOR-LAB/Synthetic Myddosome Paper/6_Manuscript/Source files/", figure)
NAME_KEY        <- fread("~/Documents/Github/Analysis_Synthethic_Myddosome/FigureScripts/Figure 4 & S6/Figure_4_ELISA_CL_KEY.csv", header = T) 

# load functions
source("~/Documents/Github/Analysis_Synthethic_Myddosome/FigureScripts/functions.R")

# process ELISA
plate_data_raw <- ELISA_Fx(Input_Directory, Output_Directory)
plate_data     <- left_join(plate_data_raw, NAME_KEY)
plate_data     <- plate_data %>% filter(CELL_LINE != "NA") %>% unique()

# ensure correct column type assignment
plate_data$CONDITION <- as.factor(plate_data$CONDITION)

################################################################################
# subset and normalize the Dose Response Data

plotting_data <- plate_data %>% group_by(CELL_LINE, CL_NAME_ON_PLOT, STIM_DAY, CONDITION, STIM_CONCENTRATION, Date, Plate)

baseline <- plotting_data %>%
  group_by(Plate) %>%
  summarise(baseline_control_value = min(Concentration))

plotting_data <- left_join(plotting_data, baseline) %>%
  mutate(Concentration_REDUCED = case_when(!is.na(baseline_control_value) ~ Concentration - baseline_control_value, TRUE ~ Concentration))

# Baseline-corrected per cell line, per condition, per stimulation and retrieve the max values to normalize for day-to-day differences.
control_mean_per_day <- plotting_data %>%
  group_by(CELL_LINE, CL_NAME_ON_PLOT, CONDITION, STIM_CONCENTRATION, Date, STIM_DAY, Plate) %>%
  reframe(Concentration_REDUCED = Concentration_REDUCED) %>%
  ungroup() %>%
  group_by(STIM_DAY) %>%
  reframe(control_MEASUREMENT = max(Concentration_REDUCED))

# Normalize the baseline-corrected values by dividing each value by the max value per stimulation day.
plotting_data <- left_join(plotting_data, control_mean_per_day) %>%
  group_by(CELL_LINE, CL_NAME_ON_PLOT, CONDITION, STIM_CONCENTRATION, Date, STIM_DAY) %>%
  mutate(Concentration_NORMALIZED = case_when(Concentration_REDUCED / control_MEASUREMENT < 0 ~ 0, TRUE ~ Concentration_REDUCED / control_MEASUREMENT),
         Relative_Intensity_mean = mean(Concentration_NORMALIZED)) %>%
  ungroup()

# Calculate the normalized means per grouped variables
plotting_means <- plotting_data %>%
  group_by(CELL_LINE, CL_NAME_ON_PLOT, 
           STIM_CONCENTRATION,
           CONDITION,
           Date, STIM_DAY, Plate,
           PLOTTING_COLOR) %>%
  distinct(Relative_Intensity_mean, STIM_DAY, .keep_all = TRUE) %>%
  ungroup()


# Perform a t-test to compare the means per cell line per concentration
concentration_values <- unique(plotting_means$STIM_CONCENTRATION)
stat.test_list       <- list()

for (concentration_val in concentration_values) {
  concentration_data <- plotting_means %>% filter(STIM_CONCENTRATION == concentration_val)
  stat_test_result   <- ggpubr::compare_means(Relative_Intensity_mean ~ CL_NAME_ON_PLOT, data = concentration_data, method = "t.test") %>% mutate(STIM_CONCENTRATION = concentration_val)
  stat.test_list[[as.character(concentration_val)]] <- stat_test_result
}
stat.test <- do.call(rbind, stat.test_list)

# Convert the STIM_CONCENTRATION column to numeric
stat.test$STIM_CONCENTRATION <- as.numeric(as.character(stat.test$STIM_CONCENTRATION))

# Order the dataframe based on the STIM_CONCENTRATION column
stat.test <- stat.test[order(-stat.test$STIM_CONCENTRATION), ]

# Create a data frame with unique CL_NAME_ON_PLOT and corresponding PLOTTING_COLOR
color_mapping <- unique(plotting_means[, c("CL_NAME_ON_PLOT", "PLOTTING_COLOR")])

# Merge the plotting_means data frame with the color_mapping data frame
plotting_means_merged <- plotting_means %>%
  left_join(color_mapping) %>%
  mutate(CL_NAME_ON_PLOT = factor(CL_NAME_ON_PLOT, levels = unique(plotting_means$CL_NAME_ON_PLOT)))

# Calculate the mean of means and standard error of the mean per cell line and per condition
plotting_stats <- plotting_data %>%
  group_by(CELL_LINE, CL_NAME_ON_PLOT, STIM_CONCENTRATION, PLOTTING_COLOR) %>%
  summarise(Relative_Intensity_sem  = sem(Relative_Intensity_mean),
            Relative_Intensity_mean = mean(Relative_Intensity_mean)) %>%
  distinct(.keep_all = TRUE)

################################################################################

# Deriving breaks from unique STIM_CONCENTRATION values
concentration_breaks <- sort(unique(plotting_stats$STIM_CONCENTRATION))
```


```{r, echo = F, warning = F, message = F}
# Plot
figure_4F_Dose_Response_ELISA <- 
  ggplot(data = plotting_stats, aes(x = STIM_CONCENTRATION, y = Relative_Intensity_mean, group = CL_NAME_ON_PLOT, fill = CL_NAME_ON_PLOT)) +
  geom_ribbon(aes(x = STIM_CONCENTRATION, 
                  ymin = Relative_Intensity_mean - Relative_Intensity_sem,
                  ymax = Relative_Intensity_mean + Relative_Intensity_sem,
                  fill = CL_NAME_ON_PLOT),
              alpha = 0.4, show.legend = F) +
  geom_path(size = 0.75, aes(col = CL_NAME_ON_PLOT)) +
  geom_text(data = subset(plotting_stats, STIM_CONCENTRATION == max(STIM_CONCENTRATION)), 
            aes(label    = gsub("CHARMS-sT6BM-", "", CL_NAME_ON_PLOT), 
                x        = max(STIM_CONCENTRATION), 
                y        = Relative_Intensity_mean,
                fontface = "bold"),
            color = setNames(unique(plotting_means_merged$PLOTTING_COLOR), unique(plotting_means_merged$CL_NAME_ON_PLOT)),
            hjust = -0.1, vjust = 0.5, size = 12) +
  labs(x = "IL-1 Conc. [ng/mL]", 
       y = "Relative Response") +
  scale_fill_manual(name  = "CL_NAME_ON_PLOT", values = setNames(unique(plotting_means_merged$PLOTTING_COLOR), unique(plotting_means_merged$CL_NAME_ON_PLOT))) +
  scale_color_manual(name = "CL_NAME_ON_PLOT", values = setNames(unique(plotting_means_merged$PLOTTING_COLOR), unique(plotting_means_merged$CL_NAME_ON_PLOT))) +
  guides(color = "none", fill = guide_legend(reverse = TRUE, ncol = 1)) +
  theme_cowplot(font_family = "Helvetica") + 
  theme(legend.position = c(0.05,0.9),
        legend.title = element_blank(),
        plot.margin = unit(c(20,20,20,20), 'mm')) +
  scale_x_log10(breaks = concentration_breaks, labels = concentration_breaks)

figure_4F_Dose_Response_ELISA
```


#### STATISTICS

##### Checking for Normal distrbution with QQ-Plots

QQ plot draws the correlation between a given data and the normal distribution.
Normal QQ plots are preferred because at larger sample sizes the Shapiro-Wilk test becomes very sensitive even to a minor deviation from normality.

```{r, echo = F, warning = F, message = F, fig.dim=c(8,2)}
pacman::p_load(tidyverse, ggpubr, rstatix)

# subset the means data
data <- plotting_means[, c("CL_NAME_ON_PLOT", "Relative_Intensity_mean", "STIM_CONCENTRATION", "PLOTTING_COLOR")]
data$CL_NAME_ON_PLOT <- gsub("CHARMS-sT6BM-", "", x = data$CL_NAME_ON_PLOT)

data$CL_NAME_ON_PLOT <- as.factor(data$CL_NAME_ON_PLOT)

concentration_values <- unique(data$STIM_CONCENTRATION)

# Create a list to store ggplot objects
qq_plots <- list()

for (concentration_val in concentration_values) {
  concentration_data <- plotting_means %>% filter(STIM_CONCENTRATION == concentration_val)
  res_aov <- aov(Relative_Intensity_mean ~ CL_NAME_ON_PLOT, data = concentration_data)
  qq_plot <- ggqqplot(res_aov$residuals, id = FALSE) +
    ggtitle(paste0("conc = ", concentration_val)) +
    theme_cowplot()
  
  qq_plots[[as.character(concentration_val)]] <- qq_plot
}

# Combine all plots into one using facet_wrap
combined_plot <- wrap_plots(qq_plots, ncol = length(concentration_values))

# Print the combined plot
print(combined_plot)

```

##### Checking for Normal distrbution with a Shapiro-Wilk Test

Check normality assumption by groups. Computing Shapiro-Wilk test for each group level. If the data is normally distributed, the p-value should be greater than 0.05.

```{r, echo = F, warning = F, message = F}

shapiro.test_list <- list()

for (concentration_val in concentration_values) {
  
  concentration_data <- plotting_means %>% filter(STIM_CONCENTRATION == concentration_val)
  
  res_aov <- aov(Relative_Intensity_mean ~ CL_NAME_ON_PLOT, data = concentration_data)
  
  # do we have normally distributed values?
  # here we assume normal distribution, so p-values > 0.05 are GOOD!
  
  shapiro_test_result <- shapiro.test(res_aov$residuals)[["p.value"]]
  shapiro.test_list[[as.character(concentration_val)]] <- shapiro_test_result
}

shapiro.test <- as.table(unlist(shapiro.test_list)) %>%
  as.data.frame() %>%
  setnames(old = c("Var1", "Freq"), new = c("STIM_CONCENTRATION", "p")) %>%
  mutate(normally_distributed = case_when(p > 0.05 ~ T, T ~ F))

shapiro.test

```


##### Checking for Homogneity of variance assumption with Levene

We will use the Levene’s test to check the homogeneity of variances.
p-value is > 0.05, which is not significant. This means that, there is not significant difference between variances across groups. Therefore, we can assume the homogeneity of variances in the different treatment groups.

```{r, echo = F, warning = F, message = F}

levene.test_list <- list()

for (concentration_val in concentration_values) {
  
  concentration_data <- plotting_means %>% filter(STIM_CONCENTRATION == concentration_val)
  
  levene <- concentration_data %>% 
    levene_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT) %>%
    mutate(STIM_CONCENTRATION = concentration_val)
  
  levene.test_list[[as.character(concentration_val)]] <- levene$p
}

levene.test <- as.table(unlist(levene.test_list)) %>%
  as.data.frame() %>%
  setnames(old = c("Var1", "Freq"), new = c("STIM_CONCENTRATION", "p")) %>%
  mutate(equal_variances = case_when(p > 0.05 ~ T, T ~ F))

levene.test
```


- 'Dn' and 'DFd' indicate the degrees of freedom in the numerator and the denominator respectively
- 'F' indicates that we are comparing to an F-distribution (F-test) and F is the obtained F-statistic value
- 'p' specifies the p-value
- 'ges' is the generalized effect size (generalized eta squared)

'ges' measures the proportion of the variability in the outcome variable (here Relative_Intensity_mean) that can be explained in terms of the predictor (here, CL_NAME_ON_PLOT). An effect size of 0.356 means that 35.6% of the change in the weight can be accounted for the treatment conditions. High concentrations have effect sizes of up to 0.968. 

Since several concentrations have significant p-values below 0.05, there are indeed significant differences between groups.


##### One-Way ANOVA & Tukey

###### ANOVA

Since our values show homogenous variances, we can safely continue to perform a normal ANOVA test.


```{r, echo = F, warning = F, message = F}

anova_test_results <- data %>%
  group_by(STIM_CONCENTRATION) %>%
  anova_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT)

# anova_test_results
subset(anova_test_results, p < 0.05)

```

###### Tukey post-hoc

A significant one-way ANOVA is generally followed up by Tukey post-hoc tests to perform multiple pairwise comparisons between groups. Key R function: tukey_hsd() [rstatix].

- estimate: estimate of the difference between means of the two groups
- conf.low, conf.high: the lower and the upper end point of the confidence interval at 95% (default)
- p.adj: p-value after adjustment for the multiple comparisons.

```{r, echo = F, warning = F, message = F}

pwc_tukey_hsd <- data %>% 
  group_by(STIM_CONCENTRATION) %>%
  tukey_hsd(Relative_Intensity_mean ~ CL_NAME_ON_PLOT)

# pwc_tukey_hsd[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")]

subset(pwc_tukey_hsd[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")], p.adj < 0.05)


```

##### Welch-ANOVA & Games-Howell

###### Welch ANOVA

In a situation where the homogeneity of variance assumption is not met, we can compute the Welch one-way ANOVA test using the function welch_anova_test()[rstatix package]. This test does not require the assumption of equal variances. It should be performed if the Levene test was significant.

```{r, echo = F, warning = F, message = F}

welch_anova_test_results <- data %>% 
  group_by(STIM_CONCENTRATION) %>%
  welch_anova_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT)

# welch_anova_test_results

subset(welch_anova_test_results, p < 0.05)

```


###### Games-Howell

Following the Welch test, the Games-Howell post hoc test or pairwise t-tests (with no assumption of equal variances) can be used to compare all possible combinations of group differences.

```{r, echo = F, warning = F, message = F}
pwc_games_howell <- data %>% 
  group_by(STIM_CONCENTRATION) %>%
  games_howell_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT)

subset(pwc_games_howell[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")], p.adj < 0.05)

```
```{r, echo = F, warning = F, message = F}

pwc_games_howell <- pwc_games_howell %>% add_xy_position(x = "CL_NAME_ON_PLOT") %>% left_join(data)

ggboxplot(data, x = "CL_NAME_ON_PLOT", y = "Relative_Intensity_mean", 
          fill = "PLOTTING_COLOR") +
  stat_pvalue_manual(pwc_games_howell, hide.ns = T) +
  labs(caption = get_pwc_label(pwc_games_howell)) +
  facet_wrap(~STIM_CONCENTRATION, nrow = 1) +
  scale_fill_identity()

```

```{r, echo = F, warning = F, message = F}

pwc_pairwise_t_test <- data %>% 
  group_by(STIM_CONCENTRATION) %>%
  pairwise_t_test(
    Relative_Intensity_mean ~ CL_NAME_ON_PLOT, 
    pool.sd = FALSE)

# pwc_pairwise_t_test[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")]

subset(pwc_pairwise_t_test[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")], p.adj < 0.05)

```

```{r, echo = F, warning = F, message = F}

pwc_pairwise_t_test <- pwc_pairwise_t_test %>% add_xy_position(x = "CL_NAME_ON_PLOT") %>% left_join(data)

ggboxplot(data, x = "CL_NAME_ON_PLOT", y = "Relative_Intensity_mean", 
          fill = "PLOTTING_COLOR") +
  stat_pvalue_manual(pwc_pairwise_t_test, hide.ns = T) +
  labs(caption = get_pwc_label(pwc_pairwise_t_test)) +
  facet_wrap(~STIM_CONCENTRATION, nrow = 1) +
  scale_fill_identity()

```



##### Kruskal-Wallis

Kruskal-Wallis test is a non-parametric alternative to the one-way ANOVA test. It extends the two-samples Wilcoxon test in the situation where there are more than two groups to compare. It’s recommended when the assumptions of one-way ANOVA test are not met.

```{r, echo = F, warning = F, message = F}
kruskal_test_results <- data %>%
  group_by(STIM_CONCENTRATION) %>%
  kruskal_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT) %>%
  mutate(p.adj.signif = case_when(p < 0.05 ~ "*", T ~ ""))

kruskal_test_results
```

From the output of the Kruskal-Wallis test, we know that there are significant differences between groups, but we don’t know which pairs of groups are different.

A significant Kruskal-Wallis test is generally followed up by Dunn’s test to identify which groups are different. It’s also possible to use the Wilcoxon’s test to calculate pairwise comparisons between group levels with corrections for multiple testing.

Compared to the Wilcoxon’s test, the Dunn’s test takes into account the rankings used by the Kruskal-Wallis test. It also does ties adjustments.

```{r, echo = F, warning = F, message = F}
pwc_dunn <- data %>% 
  group_by(STIM_CONCENTRATION) %>%
  dunn_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT) %>%
  filter(p.adj < 0.05)

pwc_dunn[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")]
```

```{r, echo = F, warning = F, message = F}

pwc_dunn <- pwc_dunn %>% add_xy_position(x = "CL_NAME_ON_PLOT") %>% left_join(data)


ggboxplot(data, x = "CL_NAME_ON_PLOT", y = "Relative_Intensity_mean", 
          fill = "PLOTTING_COLOR") +
  stat_pvalue_manual(pwc_dunn, hide.ns = TRUE) +
  labs(caption = get_pwc_label(pwc_dunn)) +
  facet_wrap(~STIM_CONCENTRATION, nrow = 1) +
  scale_fill_identity()

```

Pairwise comparisons using Wilcoxon’s test:

```{r, echo = F, warning = F, message = F}
pwc_wilcox <- data %>% 
  group_by(STIM_CONCENTRATION) %>%
  wilcox_test(Relative_Intensity_mean ~ CL_NAME_ON_PLOT)

pwc_wilcox[,c("STIM_CONCENTRATION", "p.adj", "p.adj.signif", "group1", "group2")]
```

```{r, echo = F, warning = F, message = F}

pwc_wilcox <- pwc_wilcox %>% add_xy_position(x = "CL_NAME_ON_PLOT") %>% left_join(data)

ggboxplot(data, x = "CL_NAME_ON_PLOT", y = "Relative_Intensity_mean", 
          fill = "PLOTTING_COLOR") +
  stat_pvalue_manual(pwc_wilcox, hide.ns = T) +
  labs(caption = get_pwc_label(pwc_wilcox)) +
  facet_wrap(~STIM_CONCENTRATION, nrow = 1) +
  scale_fill_identity()

```












